Malacology: A Programmable Storage System

### 2016-10-20 paper/paper.tex
comment
comments

\noindent\textbf{The Malacology Approach:} Re-use the capability management
features of the MDS.  While the batching mechanism can achieve high throughput,
it is not appropriate for applications that require predictable latency. The
throughput in Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a
centralized sequencer implementation. While throughput is lower for two clients
(because of the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.\\

@@

In Section~\ref{consistencyversioning-of-cluster-state} we described an
interface management service that is responsible for the durable and
consistent cluster-wide distribution of interface versions. We evaluate the
costs of such a service by embedding interface definitions in a Ceph cluster
membership data structure that is managed by a Paxos instance, and distributed
using a scalable, peer-to-peer gossip protocol that is built into Ceph. We
assume an architecture that consists of a light-weight interface that enforces
the semantics of interface management resulting in one or more interface
updates that must be consistent across the cluster. The following experiments
focus on the cost of achieving distribution of consistent a interface version.

@@

The first experiment shown in Figure~\ref{fig:propdelay} illustrates a lower
bound cost for updates in a large cluster by avoiding disk I/O for storing
interface updates locally within each OSD.  In the experiment labeled "120 OSD
(RAM)" a cluster of 120 OSDs (10 OSDs x 12 servers) using an in-memory data
store were deployed, showing a latency of less than 54 ms with a probability
of 90\% and a worst case latency of 194 ms. The curve labeled "3 OSD (HDD)" is
a smaller cluster where each of the three OSDs uses a spinning disk as the
object store that saves a copy of the cluster map, and shows a latency of 37
ms with a 90\% probability and a worst case latency of 255 ms. Since the cost
of a disk I/O is larger than the same I/O executed against the in-memory
device, the predominant cost in a lightly loaded cluster appears to be the
number of OSDs.

>>>>

\paa{meta point: I am not sure the "The Malacology Approach" thing works, because it
makes the reader think that we are contrasting with a strawman. I think that if we replace this with (eg)
``Malacology reuses ....'', ``Malacology pulls'', etc, it reads more smoothly.}
\noindent\textbf{The Malacology Approach:} Re-use the capability management
features of the MDS.  While the batching mechanism can achieve high throughput,
it is not appropriate for applications that require predictable latency. The
throughput in Figure~\ref{fig:captp} labeled $2C,ZLog$ corresponds to a
centralized sequencer implementation. While throughput is lower for two clients
(because of the synchronous network round-trip required for each request),
Figure~\ref{fig:capcdf} shows that this approach achieves more predicable
latency compared to all other approaches except for the single client locally
cached mode.\\

\paa{there should probably be a sum-up sentence here; eg Malacology exposes knobs that
allow application programmers to tune the storage system to the needs of their application.}

@@

In Section~\ref{consistencyversioning-of-cluster-state} we described an
interface management service that is responsible for the durable and
consistent cluster-wide distribution of interface versions. We evaluate the
costs of such a service by embedding interface definitions in a Ceph cluster
membership data structure that is managed by a Paxos instance, and distributed
using a scalable, peer-to-peer gossip protocol that is built into Ceph. We
assume an architecture that consists of a light-weight interface that enforces
the semantics of interface management resulting in one or more interface
updates that must be consistent across the cluster. \paa{the word ``interface''
occurs too many times in the last sentence, but I'm not sure how to fix it.}
The following experiments
focus on the cost of distributing a consistent interface version.

@@

The first experiment shown in Figure~\ref{fig:propdelay} illustrates a lower
bound cost for updates in a large cluster by avoiding disk I/O for storing
interface updates locally within each OSD.  In the experiment labeled "120 OSD
(RAM)" a cluster of 120 OSDs (10 OSDs x 12 servers) using an in-memory data
store were deployed, showing a latency of less than 54 ms with a probability
of 90\% and a worst case latency of 194 ms. The curve labeled "3 OSD (HDD)" 
\paa{DANGER -- didn't we delete this?}
is
a smaller cluster where each of the three OSDs uses a spinning disk as the
object store that saves a copy of the cluster map, and shows a latency of 37
ms with a 90\% probability and a worst case latency of 255 ms. Since the cost
of a disk I/O is larger than the same I/O executed against the in-memory
device, the predominant cost in a lightly loaded cluster appears to be the
number of OSDs.
